---
title: "Data.Cleaning"
author: "Anna von Bachmann"
date: '2022-05-06'
output: html_document
---


```{r}
#data upload
tcga_exp = readRDS("../data/tcga_tumor_log2TPM.RDS")
tcga_annot = readRDS("../data/tcga_tumor_annotation.RDS")
tcga_tumor_norm = readRDS("../data/tcga_tumor_normal_datascience_proj_2022.RDS")
genesets = readRDS("../data/hallmarks_genesets.rds")
```

```{r}
<<<<<<< HEAD
#check for NAs
sum(is.na(tcga_exp))
#as the sum equals zero, there are no missing values in this data frame
```


```{r}
#if there is no difference between min and max of expression counts --> genes will be removed
min.count.gene = apply(tcga_exp, 1, min)
max.count.gene = apply(tcga_exp, 1, max)
sum(which(min.count.gene == max.count.gene)) #to see how many genes show no difference in expression
tcga_exp = tcga_exp[-which(min.count.gene == max.count.gene)] #to remove these genes from the data set
# how to find genes with low variance?? which threshold?? 
```

=======
#check for N/As
sum(is.na(tcga_exp))
#as the sum equals zero, there are no missing values in this data frame 
```
```{r}
#if there is no difference between min and max of expression counts --> genes will be removed
min.count.gene = apply(tcga_exp, 1, min)
message("Hi")
max.count.gene = apply(tcga_exp, 1, max)
message("Hi1")
sum(which(min.count.gene == max.count.gene)) 
message("Hi2")  #to see how many genes show no difference in expression
tcga_exp_variable_only = tcga_exp[-which(min.count.gene == max.count.gene)]#to remove the genes from these genes from the data set

#how to find genes with low variance? Which threshold?
```


>>>>>>> c9c710522fb2910d1b91958bc1ef0d5e0f595ebd
